Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-11-02 paper.tex
update

\subsection{Fitness Calculation}
The fitness value of a service composition solution is a weighted sum of all the quality components discussed previously shown in Formula \ref{equation6}, in which fitness value of 1 means the best comprehensive quality and 0 means the worst. As the sum of all the components' weights ($w_1$ to $w_6$) equals to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1. Also, the lowest T and C value represent the best component quality so that the objective function can be offset using $(1 - T)$ and $(1 - C)$.

\begin{equation}
\label{equation6}
Fitness = w_1MT + w_2S + w_3A + w_4R + w_5(1 - T) + w_6(1 - C)
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$

@@

The overall algorithm investigated here is a PSO-based web service composition algorithm \ref{novelSteps} from   \cite{da2016particle} with a different decoded algorithm \ref{graph_building} to generate a composition weighted graph from a queue. In the first algorithm, the idea is to translate the particle location into a service queue as an indirect representation of composition weighted graph, so finding the best fitness of the composite service solution is to discover the optimised location of the particle. In PSO, the dimension of the particle is set up as the same as the number of relevant web services, and all the services index is mapped to the location in a particle, and we put services in a queue in ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}. We select and connect web services to the start Vetex from the service queue if the web service can satisfy the given $T_{input}$. Meanwhile, an Output Set is initialised and kept being updated using outputs from the new-added web services in the graph, later on, more services are connected if services' inputs could be satisfied by any output in the Output Set. At last, The end vetex is connected if the updated Output Set contains the $T_{output}$. In addition, dangle service nodes and edges should be removed.

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach, and to explore the impacts of the semantic matchmaking that contributes to overall composition quality, and to compare solutions generated by QoS-ware approach with our method.

We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform a standard evaluation. WSC09 provides problems,  WSDL+MECE, taxonomy files in formats of xml, xml, and owl respectively, where five tasks consisted in with variable size in both services, and ontologies. Therefore, it is a proper dataset for the scalability measures in our defined quality evaluation model. Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services in each data set is shown in the second, third, fourth column respectively. Also, we extend all the datasets with QoS attributes from service providers to perform a comprehensive quality evaluation. 
\begin{table}[]
\centering
\caption{Features of the WSC09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC09 01                     & 1578       &3102           &572      \\ \hline
WSC09 02                     & 12388      &24815          &4129      \\ \hline
WSC09 03                     & 18573      &37316          &8138      \\ \hline
WSC09 04                     & 18673      &37324          &8301      \\ \hline
WSC09 05                     & 31044      &62132          &15211    \\ \hline
\end{tabular}
\end{table}

We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. Experimentation was done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}. The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the relevant service size shown in graph. we run 30 times independently for each dataset. In addition, weights setting are flexibly defined by users' preferences. As part of their requirement, we configure weights of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.

\section{Results and Analysis}\label{results_analysis}
\subsection{Convergence Test}\label{convergenceTest}

\subsection{Comparision Test}\label{comparisionTest}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{wscs.pdf}}}
 \caption{Example composition solutions for problem1 WSC'09.}
 \label{wscs}
\end{figure}
We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated with two values of matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},... e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition solution to task 1, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively. In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined before. The demonstration of the solution is to make better comparison of results using the same solution model from different approaches .

@@

>>>>

\subsection{Fitness Calculation}
The fitness value of a service composition solution is a weighted sum of all the quality components discussed previously shown in Formula \ref{equation6}, in which fitness value of 1 means the best comprehensive quality and 0 means the worst. As the sum of all the components' weights ($w_1$ to $w_6$) equals to 1, $MT$, $S$, $A$, $R$, $T$, and $C$ must be normalised so that the fitness value falls within the range from 0 to 1. Also, the lowest T and C value represent the best component quality so that the objective function can be offset using $(1 - T)$ and $(1 - C)$ using normalisation formula \ref{equation8}, and normalisation formula \ref{equation7} is for the rest components. Therefore, the whole problem is treated as a maximisation problem.

\begin{equation}
\label{equation6}
Fitness = w_1MT + w_2S + w_3A + w_4R + w_5(1 - T) + w_6(1 - C)
\end{equation}
\noindent where $\sum_{i=1}^{6} w_i = 1$
\\\\
\begin{equation}
\label{equation7}
normalise(value) = 
\begin{cases}
	\frac{value - min}{max - min} & \text{ if }max - min \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}
\begin{equation}
\label{equation8}
normalise(value) = 
\begin{cases}
	\frac{max - value}{max - min} & \text{ if }max - min \neq 0.\\
	1 & \mathrm{ otherwise}.
\end{cases}
\end{equation}

@@

The overall algorithm investigated here is a PSO-based web service composition algorithm \ref{novelSteps} from   \cite{da2016particle} with a different decoded algorithm \ref{graph_building} to generate a composition weighted graph from a queue. In the first algorithm, the idea is to translate the particle location into a service queue as an indirect representation of composition weighted graph, so finding the best fitness of the composite weighted graph is to discover the optimised location of the particle in the search space. In PSO, the dimension of the particle is set up as the same number as relevant web services, and the index of services is mapped to the location vectors in a particle, and we put services in a queue in ascending order, from which we decode a weighted graph using Algorithm \ref{graph_building}. We select and connect  service vertex to the start vertex from the service queue if the web service can satisfy the output of start vertex. Meanwhile, an Output Set is initialised and kept being updated using outputs from the new-added service vertex in the weighted graph, later on, more services vertex are connected with edges if services' inputs could be satisfied by any output in the Output Set. At last, The end vertex is connected if the updated Output Set contains all end inputs. In addition, dangling service vertex and edges should be removed.

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are $(1)$ to measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach, $(2)$ to explore the impacts of the semantic matchmaking that contributes to overall composition quality, and $(3)$ to compare solutions generated by QoS-ware approach with our method.

We utilise benchmark dataset web service challenge 2009 (WSC09) \cite{kona2009wsc} to perform a evaluation. WSC09 provides problems where five tasks consisted in with variable size in both services, and ontologies. Therefore, it is a proper dataset for the scalability measures in our defined quality evaluation model. Table \ref{wsc09datasetTable} presents the features of the WSC’09 dataset. The number of concepts, individuals in the ontology and services in each data set is shown in the second, third, fourth column respectively. Also, we extend all the datasets with QoS attributes from service providers to enable our evaluation. 
\begin{table}[]
\centering
\caption{Features of the WSC09 datasets}
\label{wsc09datasetTable}
\begin{tabular}{|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{Dataset} & No.Concept & No.Individual & No.Service \\ \hline
WSC09 01                     & 1578       &3102           &572      \\ \hline
WSC09 02                     & 12388      &24815          &4129      \\ \hline
WSC09 03                     & 18573      &37316          &8138      \\ \hline
WSC09 04                     & 18673      &37324          &8301      \\ \hline
WSC09 05                     & 31044      &62132          &15211    \\ \hline
\end{tabular}
\end{table}

We run the experiment under computing grid comprising of almost 170 NetBSD (Unix operating system) workstations operated by the Sun Grid Engine. Experimentation is done using the approach explained in Section \ref{qswsc_approach}, and evaluated in the comprehensive quality model introduced in Subsection \ref{qualityModel}. The parameters were chosen based on general settings from \cite{shi2001particle} for our PSO-based approach, 30 particles evolved in 100 generations in the searching space, in which problem dimension's size equals to the number of relevant services in service repository. We run 30 times independently for each dataset. In addition, weight settings are flexibly defined by users' preferences. As part of their requirement, we configure weight of fitness function to properly balance functional side and nonfunctional side. Therefore, $w_{1}$ and $w_{2}$ are equals to 0.1 and 0.4,  and $w_{3}$, $w_{4}$, $w_{5}$, $w_{6}$ are all set to 0.125 accordingly.

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparision Test}\label{comparisionTest}
\begin{figure}[h]
\centerline{
\fbox{
\includegraphics[width=8cm]{wscs.pdf}}}
 \caption{Example composition solutions for problem1 WSC'09.}
 \label{wscs}
\end{figure}
We defined our optimised web service composition as $WSC = (V, E)Graph$, where $V$ is a set of services as vertex: $V=[S1, S2...Sn]$ and $E$ is a set of service connections as edges associated with two values of matchType quality and semantic similarity quality: $E = {e_{1}, e_{2},... e_{n}}$ where $e1$ is define as $(S_{1},S_{2})={q_{mt}, q_{s}}$. Here we provide an example of the web service composition solution to task 1, which can be described in the Figure \ref{wscs}. The data of composite web service flows from the start to the end, where five web services involved and linked with each other using edge connections. Besides that, $q(s_{mt})$ and $q(s_{s})$ are calculated for all edges ${e_{1}, e_{2},... e_{n}}$, and further aggregated in $Q_{mt}$ and $Q_{s}$ respectively. In addition, $Q_{QoS}$ is calculated by all the non-functional attributes of $V$ using aggregation rules defined before. The demonstration of the solution is to make better comparison of results using the same solution model from different approaches .

@@

\subsection{Convergence Test}\label{convergenceTest}
